### 2020-03-09 ms/ms.tex
Incorporate Julien's edits

Reductions in fishing mortality, albeit necessary, are not always sufficient
to facilitate population recovery. Experience with numerous commercially
exploited marine fisheries since the early 1990s has shown that not all
populations respond as favourably as anticipated to major reductions in
exploitation \citep{Hutchings2017}. Efforts to close commercial
Atlantic salmon (\emph{Salmo salar}) fisheries in eastern Canada culminated in
moratoria in all regions, beginning in the Maritime provinces (1984) and
following in Newfoundland (1992), Labrador (1998), and Qu\'{e}bec (2000). Since
these closures, many populations have not increased as 
expected \citep{Dempson2004, ICES2019}; some 
have been assessed as considered threatened or endangered by the 
Committee on the Status of Endangered Wildlife in Canada \citep[][]{Cosewic2010}, 
Canada's national science advisory body (to the national government) on
species risk of extinction.
While it is not fully understood what is driving population declines, the potential
drivers of these are many \citep[see ][for a detailed discussion of possible
causes]{Cairns2001}, including but not limited to: fishing mortality \citep{Dempson2004}, 
damming of waterways and changes in the freshwater habitat \citep{Dunfield1985}, acidification
\citep[particularly in the Southern Uplands region of
NS, see][]{Gibson2010}, predation by seals and birds \citep{Cairns2000}, negative
effects of interbreeding or interactions with escaped farmed salmon
\citep{Keyser2018}, and climate-driven changes in survival and productivity \citep{Mills2013}.

@@

Smolt and adult return abundance estimates originate from a variety of
sources. Smolt estimates from the ... and Conne populations were obtained using a
mark-recapture approach, while estimates from the ..., WAB, and Campbellton populations
were obtained by direct counts using fish counting fences.
For further details on the data collection methodologies refer to 
\citet{Dempson1991, Venoitt2018} for NL populations, 
\citet{April2018}  for QC populations,
\citet{Jones2014} for NB populations,
and \citet{Gibson2009} for NS populations.

Yearly return data are recorded in terms of two size groups: small ($< 63$ cm
FL) and large ($\geq 63$ cm FL) salmon, as these closely represent different
life-history strategies (i.e. 1SW and 2SW), but can be confounded with repeat
spawners of different sizes. To correct for this, we estimated the abundance
of 1SW and 2SW returns using yearly scale age data of a subsample of returns:

@@

% 2. How they compare to other publications
Our results are contrary to those of \citet{Olmos2019}, who detected positive
correlations in post-smolt survival among spatially broad stock units. These differences
could be due to a number of reasons: different model specifications and
structure, different methods for estimating covariance, difference in the
spatial scales of data sources, and perhaps most importantly the use stock-recruitment relationships
rather than empirical smolt count data to estimate marine survival.
As trends in marine survival during the first winter at sea are highly independent
among rivers on relatively small spatial scale, trends from broader
geographical areas (i.e. province, state, or country-wide estimates) may not
be representative.
Interestingly, our estimates of \So and \St are very similar to those produced
by \citet{Chaput2003b}, and our trends are almost identical for the
overlapping time period that marine survival was estimated for in their study
(1984-1998). 
While \citet{Chaput2003b} separated abundance data for males and females
and assumed their survival rates were the same (to be able to reach an
analytical solution), our study reached almost the same results (albeit with
slightly higher uncertainty), using a Bayesian approach with informative
priors. These overlapping trends obtained with two different methods 
suggest that our method is effective at estimating marine survival.

>>>>

Reductions in fishing mortality, albeit necessary, are not always sufficient
to facilitate population recovery. Experience with numerous commercially
exploited marine fisheries since the early 1990s has shown that not all
populations respond as favourably as anticipated to major reductions in
exploitation \citep{Hutchings2017}. Gradual efforts to close commercial
Atlantic salmon (\emph{Salmo salar}) fisheries in eastern Canada culminated in
full moratoria in all regions, beginning in the Maritime provinces (1984) and
following in Newfoundland (1992), Labrador (1998), and Qu\'{e}bec (2000). Since
these closures, many populations have not increased as 
expected \citep{Dempson2004, ICES2019}; some 
have been assessed as considered threatened or endangered by the 
Committee on the Status of Endangered Wildlife in Canada \citep[][]{Cosewic2010}, 
Canada's national science advisory body (to the national government) on
species risk of extinction.
While it is not fully understood what is driving population declines, the potential
drivers of these are many \citep[see ][for a detailed discussion of possible
causes]{Cairns2001}, including but not limited to: fishing mortality \citep{Dempson2004}, 
damming of waterways and changes in the freshwater habitat \citep{Dunfield1985}, acidification
\citep[particularly in the Southern Uplands region of
NS, see][]{Gibson2010}, predation by seals and birds \citep{Cairns2000}, negative
effects of interbreeding or interactions with escaped farmed salmon
\citep{Keyser2018}, and climate-driven changes in survival and productivity \citep{Mills2013}.

@@

Smolt and adult return abundance estimates originate from a variety of
sources. Smolt estimates from the Trinit\'{e}, Saint-Jean, and Conne populations were obtained using a
mark-recapture approach, while estimates from the ..., WAB, and Campbellton populations
were obtained by direct counts using fish counting fences.
For further details on the data collection methodologies refer to 
\citet{Dempson1991, Venoitt2018} for NL populations, 
\citet{April2018}  for QC populations,
\citet{Jones2014} for NB populations,
and \citet{Gibson2009} for NS populations.

Yearly return data are often recorded in terms of two size groups: small ($< 63$ cm
FL) and large ($\geq 63$ cm FL) salmon, as these closely represent different
life-history strategies (i.e. 1SW and 2SW), but can be confounded with repeat
spawners of different sizes. To correct for this in returns 
reported as small and large salmon, we estimated the abundance
of 1SW and 2SW returns using yearly scale age data of a subsample of returns:

@@

% 2. How they compare to other publications
Our results are contrary to those of \citet{Olmos2019}, who detected positive
correlations in post-smolt survival among spatially broad stock units. These differences
could be due to a number of reasons: different model specifications and
structure, different methods for estimating covariance, difference in the
spatial scales of data sources (i.e. river vs province scales), and perhaps most importantly the use stock-recruitment relationships
rather than empirical smolt count data to estimate marine survival.
As trends in marine survival during the first winter at sea are highly independent
among rivers on relatively small spatial scale, trends from broader
geographical areas (i.e. province, state, or country-wide estimates) may not
be representative.
Interestingly, our estimates of \So and \St are very similar to those produced
by \citet{Chaput2003b}, and our trends are almost identical for the
overlapping time period that marine survival was estimated for in their study
(1984-1998). 
While \citet{Chaput2003b} separated abundance data for males and females
and assumed their survival rates were the same (to be able to reach an
analytical solution), our study reached almost the same results (albeit with
slightly higher uncertainty), using a Bayesian approach with informative
priors. These overlapping trends obtained with two different methods 
suggest that our method is effective at estimating marine survival.
